|

### 2023-02-05 manuscript/supplementary.Rmd
one more update

---
title: | 
  | Supplementary material for
  | A novel high-power test for continuous outcomes truncated by death
author: | 
  | Andreas Kryger Jensen and Theis Lange
  | Section of Biostatistics, Department of Public Health, University of Copenhagen
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: | 
  | Supplementary material for
  | A novel high-power test for continuous outcomes truncated by death
author: | 
  | Andreas Kryger Jensen and Theis Lange
  | Section of Biostatistics, Department of Public Health
  | University of Copenhagen
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
